Adolescent well-being in the digital age

### 2022-05-04 00-clean.Rmd
Switch from GLOBE to WB regions

## GLOBE regions

We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised. This allows us to eg. present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models. We use the extended GLOBE regions following Jebb et al. (2020), and had to manually add labels to some countries that were not grouped in those studies.

```{r globe-regions}
#| results: hold
#| label: tbl-globe
#| tbl-cap: "Countries with manually filled region"

regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>%
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(country = str_remove_all(country, "\\*")) %>%
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(country = countryname(country)) %>%
  drop_na(country)

# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
regions <- distinct(regions, region, country)

# Countries in GBD not present in region data
no_region_gbd <- filter(
  distinct(gbd, country),
  !(country %in% unique(regions$country))
) %>%
  arrange(country)

# Then see what countries in GWP are without region
no_region_gwp <- filter(
  distinct(gwp, country),
  !(country %in% unique(regions$country))
) %>%
  arrange(country)

bind_rows(no_region_gbd, no_region_gwp) %>%
  arrange(country) %>%
  distinct() %>%
  write_csv("data-raw/Regions/countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein

# Load our manually filled region data
regions_filled <- read_csv(
  "data-raw/Regions/countries-without-region-filled.csv"
)

# Combine Jebb et al GLOBE regions and our manually added ones
regions <- regions %>%
  bind_rows(
    regions_filled %>%
      mutate(Note = "Filled")
  ) %>%
  arrange(region, country)

# Shorter name for plots
regions <- regions %>%
  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))

# Display table of regions and countries
regions %>%
  drop_na(Note) %>%
  select(-Note) %>%
  arrange(region, country) %>%
  kbl(caption = "Countries with a manually filled region") %>%
  kable_custom()

# Clean region labels
regions$region <- str_replace_all(regions$region, " ", "_")
regions$region <- factor(regions$region)

# Remove unnecessary items
regions <- select(regions, -Note)

@@

# Remove now unnecessary variables
rm(no_region_gbd, no_region_gwp, regions_filled, regions)
```

>>>>

## Regions

>continent: "Continent as defined in the World Bank Development Indicators"

```{r}
regions <- bind_rows(
  distinct(itu, country),
  distinct(gbd, country),
  distinct(gwp, country)
) %>% 
  distinct() %>% 
  mutate(
    region = countrycode(
      country, 
      origin = "country.name", 
      destination = "continent"
    )
  )

# Manually fix two countries
regions <- regions %>% 
  mutate(
    region = if_else(country == "Kosovo", "Europe", region),
    region = if_else(country == "Nagorno Karabakh", "Asia", region)
    )

@@

regions %>% 
  group_by(region) %>%
  summarise(
    N = n(),
    Countries = str_c(country, collapse = ", ")
  ) %>% 
  kbl(caption = "Regions") %>% 
  kable_custom()
```
